---
title: "Salinity Figures - Sites 1-9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(cowplot)
library(devtools)
library(ggpubr)
library(grid)
library(gridExtra)
library(lattice)
library(marelac)
library(scales)
library(waterData)
library(hydroTSM)

```
Displayed are the figures for the nine sensor sites, spatially arranged in the order they lay near the Lone Cabbage Reef from North to South and West to East.    
Sites 1 and 3 are recorded hourly by Diver sensors. Sites 2,4,5,6,7,8, and 9 are recorded hourly by Star-Oddi sensors.    
Water discharge data provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).      
Salinity is calculated by conductivity and temperature measurements.    


```{r importdata, include=FALSE, eval=TRUE}

LC_WQ1 <- read.csv("data/LC_WQ1_All_Days_R.csv", header= T)
LC_WQ2 <- read.csv("data/LC_WQ2_All_Days_R.csv", header= T)
LC_WQ3 <- read.csv("data/LC_WQ3_All_Days_R.csv", header= T)
LC_WQ4 <- read.csv("data/LC_WQ4_All_Days_R.csv", header= T)
LC_WQ5 <- read.csv("data/LC_WQ5_All_Days_R.csv", header= T)
LC_WQ6 <- read.csv("data/LC_WQ6_All_Days_R.csv", header= T)
LC_WQ7 <- read.csv("data/LC_WQ7_All_Days_R.csv", header= T)
LC_WQ8 <- read.csv("data/LC_WQ8_All_Days_R.csv", header= T)
LC_WQ9 <- read.csv("data/LC_WQ9_All_Days_R.csv", header= T)
```

```{r columns_1and3, include=FALSE}
#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(LC_WQ1) <- c("DateTime_Serial", "Pressure", "Temperature", "Conductivity")
colnames(LC_WQ3) <- c("DateTime_Serial", "Pressure", "Temperature", "Conductivity")

```

```{r renamecolumns, include=FALSE}
#Renaming columns 
colnames(LC_WQ2) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
colnames(LC_WQ4) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
colnames(LC_WQ5) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
colnames(LC_WQ6) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
colnames(LC_WQ7) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
colnames(LC_WQ8) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
colnames(LC_WQ9) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")

```

```{r datechange, include=FALSE, warning= FALSE, message=FALSE, results="hide", eval=TRUE}

#Changing the format of the dates to be able to plot against time
LC_WQ1$newDate <- as.POSIXct(as.Date(LC_WQ1$DateTime_Serial,origin= "1899-12-30"))
LC_WQ2$newDate <- as.POSIXct(as.Date(LC_WQ2$DateTime_Serial,origin= "1899-12-30"))
LC_WQ3$newDate <- as.POSIXct(as.Date(LC_WQ3$DateTime_Serial,origin= "1899-12-30"))
LC_WQ4$newDate <- as.POSIXct(as.Date(LC_WQ4$DateTime_Serial,origin= "1899-12-30"))
LC_WQ5$newDate <- as.POSIXct(as.Date(LC_WQ5$DateTime_Serial,origin= "1899-12-30"))
LC_WQ6$newDate <- as.POSIXct(as.Date(LC_WQ6$DateTime_Serial,origin= "1899-12-30"))
LC_WQ7$newDate <- as.POSIXct(as.Date(LC_WQ7$DateTime_Serial,origin= "1899-12-30"))
LC_WQ8$newDate <- as.POSIXct(as.Date(LC_WQ8$DateTime_Serial,origin= "1899-12-30"))
LC_WQ9$newDate <- as.POSIXct(as.Date(LC_WQ9$DateTime_Serial,origin= "1899-12-30"))

```

```{r salcal, warning= FALSE,  message=FALSE, results="hide", include=FALSE}

library(marelac)

standard= 42.914

LC_WQ1$Salinity <- convert_RtoS(LC_WQ1$Conductivity/standard, 
                                t= LC_WQ1$Temperature, p= 0)
LC_WQ2$Salinity <- convert_RtoS(LC_WQ2$Conductivity/standard, 
                                t= LC_WQ2$Temperature, p=0)
LC_WQ3$Salinity <- convert_RtoS(LC_WQ3$Conductivity/standard, 
                                t= LC_WQ3$Temperature, p= 0)
LC_WQ4$Salinity <- convert_RtoS(LC_WQ4$Conductivity/standard, 
                                t= LC_WQ4$Temperature, p=0)
LC_WQ5$Salinity <- convert_RtoS(LC_WQ5$Conductivity/standard, 
                                t= LC_WQ5$Temperature, p=0)
LC_WQ6$Salinity <- convert_RtoS(LC_WQ6$Conductivity/standard, 
                                t= LC_WQ6$Temperature, p=0)
LC_WQ7$Salinity <- convert_RtoS(LC_WQ7$Conductivity/standard, 
                                t= LC_WQ7$Temperature, p=0)
LC_WQ8$Salinity <- convert_RtoS(LC_WQ8$Conductivity/standard, 
                                t= LC_WQ8$Temperature, p=0)
LC_WQ9$Salinity <- convert_RtoS(LC_WQ9$Conductivity/standard, 
                                t= LC_WQ9$Temperature, p=0)

```


```{r riverdisharge, warning= FALSE,  message=FALSE, results="hide" , include=FALSE}

#Station to analyze, can be changed to another station
station = '02323500'   

#Get site name to use in plot titles and such
stinfo  = siteInfo(station)

#Read entire time series, might take several minutes
dis   = importDVs(staid=station,code='00060',stat='00003', sdate= "1950-01-01") 

#Getting some date components
dis$year    = as.numeric(strftime(dis$dates,format="%Y"))
dis$month   = as.numeric(strftime(dis$dates,format="%m")) 

```

```{r rddate, warning= FALSE,  message=FALSE, results="hide", include=FALSE}

#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(dis) <- c("StaID", "Values", "Date", "QualCode", "Year", "Month")
head(dis)

#Changing the format of the dates to be able to plot against time
dis$newDate <- as.POSIXct(as.Date(dis$Date,origin= "1899-12-30"))

```


```{r allplots, warning= FALSE,  message=FALSE,include=FALSE}

Var1 <- #saving the plot under a name, in this case it is "Var1"
  ggplot(data= LC_WQ1, aes(x= newDate)) + #add the data file name, and describe the aesthetics using aes(x=, y=), we specify the y-axis in later script
  ggtitle("Site 1") + #creating a title for the plot
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") + #changing the labels for the x and y- axis
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) + #the ribbon creates a shadow area for the river discharge, and the y values are a fraction of the actual data, which will be corrected when we add our secondary axis
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") + #plotting points for the y-axis of Temperature
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") + #plotting points for the y-axis of Salinity
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) + #creating a secondary y-axis for the river discharge that is portional to the fraction of the river discharge we calculated before
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) + #the end date will need to be changed for every new sensor servicing, the dates are in YYYY-MM-DD, the date breaks are by 'week' but can be monthly or daily
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70) #the theme is specifically formatted to be saved as a large .tiff image, this can be edited to a different size graph

Var2 <-
  ggplot(data= LC_WQ2, aes(x= newDate)) +
  ggtitle("Site 2") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var3 <-
  ggplot(data= LC_WQ3, aes(x= newDate)) +
  ggtitle("Site 3") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var4 <-
  ggplot(data= LC_WQ4, aes(x= newDate)) +
  ggtitle("Site 4") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var5 <-
  ggplot(data= LC_WQ5, aes(x= newDate)) +
  ggtitle("Site 5") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var6 <-
  ggplot(data= LC_WQ6, aes(x= newDate)) +
  ggtitle("Site 6") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var7 <-
  ggplot(data= LC_WQ7, aes(x= newDate)) +
  ggtitle("Site 7") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var8 <-
  ggplot(data= LC_WQ8, aes(x= newDate)) +
  ggtitle("Site 8") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

Var9 <-
  ggplot(data= LC_WQ9, aes(x= newDate)) +
  ggtitle("Site 9") +
  labs(x= "Date", y= "Temp(C) & Salinity (ppt)") +
  geom_ribbon(data= dis, aes(x= newDate, y=Values/1000, ymin=0, ymax=Values/1000, fill= "blue"), fill= "cornflowerblue", alpha=0.5) +
  geom_point(aes(y= Temperature, colour= "Temperature"), color= "red") +
  geom_point(aes(y= Salinity, colour= "Salinity"), color= "#000000") +
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("2 weeks") ,
    labels = date_format("%m/%d"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-04-10"))) +
  theme(panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        aspect.ratio = 0.70)

```

```{r legendplot, warning= FALSE,  message=FALSE, include=FALSE}

#Creating a "false" plot with a correct legend

library(cowplot)

legend <- 
  ggplot(data= LC_WQ1,aes(x= newDate)) +
  geom_point(aes(y= Salinity, fill= "Salinity (ppt)  "), color= "#999999") +
  geom_point(aes(y= Temperature, fill= "Temperature (C)   "), color= "#000000") +
  geom_point(data= dis, aes(x= newDate, y=Values/1000, fill= "River Discharge (cfs)  "), color="cornflowerblue", size=2, show.legend = TRUE, pch=15, alpha=0.4) +
  guides(fill= guide_legend(show= TRUE, title="", override.aes= list(colour= c("cornflowerblue", "#000000", "red"), size=15))) +
  scale_y_continuous(sec.axis = sec_axis(~.*600, name = "River Discharge (cfs)  "), limits=c(0,40)) +
  theme(legend.position = "bottom", legend.text=element_text(size=35))

#creating a legend, to "grob" later in the final `ggdraw`
legend_b <- get_legend(legend + theme(legend.position="bottom"))
```


```{r ggdrawplot, warning= FALSE,  message=FALSE, include=FALSE}

varall<-
  ggdraw() +
  draw_plot(Var3, x=0.34, y=0, width=0.3, height=0.30 ) +
  draw_plot(Var2, x=0.34, y=0.30, width=0.3, height=0.30 ) +
  draw_plot(Var1, x=0.34, y=0.60, width=0.3, height=0.30 ) +
  draw_plot(Var4, x=0, y=0, width=0.3, height=0.30 ) +
  draw_plot(Var5, x=0, y=0.3, width=0.3, height=0.30 ) +
  draw_plot(Var6, x=0, y=0.6, width=0.3, height=0.30 ) +
  draw_plot(Var9, x=0.67, y=0, width=0.3, height=0.30 ) +
  draw_plot(Var8, x=0.67, y=0.3, width=0.3, height=0.30 ) +
  draw_plot(Var7, x=0.67, y=0.6, width=0.3, height=0.30 ) +
  draw_grob(legend_b, 0.9/2.5, 0.75, 2/9, 0.4, scale=0.5) 


```

```{r finalplot, echo=FALSE, fig.width=35,fig.height=25, dpi= 200, warning= FALSE,  message=FALSE}
varall

```