---
title: "Salinity Site Comparison"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("dplyr")
library("ggplot2")
library("grid")
library("ggthemes")
library("lattice")
library("lubridate")
library("marelac")
library("scales")
library("tidyverse")
library("waterData")

```
Displayed are the figures for the nine sensor sites, spatially arranged in the order they lay near the Lone Cabbage Reef from North to South and West to East.    
Sites 1 and 3 are recorded hourly by Diver sensors. Sites 2,4,5,6,7,8, and 9 are recorded hourly by Star-Oddi sensors.    
Water discharge data provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).      
Salinity is calculated by conductivity and temperature measurements.    


```{r importdata, include=FALSE}

wq <- read.csv("data/wq.csv", header= T)
wq$Date<- as.POSIXct(wq$Date, tz="EST",usetz=TRUE)
wq<-wq %>% 
  filter(!(Site == 0))

```


```{r dis, warning= FALSE,  message=FALSE, results="hide" , include=FALSE}

#Station to analyze, can be changed to another station
station = '02323500'   

#Get site name to use in plot titles and such
stinfo  = siteInfo(station)

#Read entire time series, might take several minutes
dis   = importDVs(staid=station,code='00060',stat='00003', sdate= "1950-01-01") 

#Getting some date components
dis$year    = as.numeric(strftime(dis$dates,format="%Y"))
dis$month   = as.numeric(strftime(dis$dates,format="%m")) 

```


```{r discol, warning= FALSE,  message=FALSE, results="hide", include=FALSE}

#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(dis) <- c("StaID", "Values", "oldDate", "QualCode", "Year", "Month")
head(dis)

#Changing the format of the dates to be able to plot against time
dis$Date <- as.POSIXct(as.Date(dis$oldDate,origin= "1899-12-30"))

```


```{r wq, warning= FALSE,  message=FALSE,include=FALSE}

wq$facet = factor(wq$Site, levels = c("6", "1", "7", "5", "2", "8","4", "3", "9"))
  

wqplot<-ggplot(data=wq, aes(x=Date))+
    labs(x= "Date", y= "Temp(C) & Salinity (ppt)", fill ="")+
  geom_ribbon(data= dis, aes(y=Values/1000, ymin=0, ymax=Values/1000, fill= "River Discharge"), color= "cornflowerblue", alpha=0.5) +
    geom_point(aes(y= Temperature, fill= "Temperature"),color= "red")+
    geom_point(aes(y= Salinity, fill= "Salinity"),color= "black")+
  scale_y_continuous(sec.axis = sec_axis(~.*1000, name = "River Discharge (cfs)"), limits=c(0,40)) + 
  scale_x_datetime(
    breaks = date_breaks("4 weeks") ,
    labels = date_format("%Y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-07-30"))) +
  scale_fill_manual(values = c("cornflowerblue", "black", "red"),guide = guide_legend(show = TRUE)) +
  theme(legend.position=("top"),
    panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        plot.title =element_text(size=30, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~facet)
```

```{r wqplot, warning= FALSE, fig.width=12,fig.height=9, echo=FALSE}
wqplot
```

