---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("cowplot")
library("dplyr")
library("ggplot2")
library("grid")
library("ggthemes")
library("lattice")
library("lubridate")
library("marelac")
library("ncdf4")
library("rnoaa")
library("plotly")
library("scales")
library("tidyverse")
library("waterData")
```

#Site 9
####Longitude:  -83.08271
####Latitude:    29.23215


The main plot consists of continuous data gathered from a Star-Oddi sensor, which measures salinity, temperature, and conductivity hourly, since November 2017.           
Water discharge data are provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).                    
Wind speed data are provided by package `rnoaa`.                       
There no are discrete measurements for this site.         
This figure is available for zoomability.     


```{r r_site, include= FALSE}
##### Site 1 Analysis with Diver sensor

wq <- read.csv("data/wq.csv", header= T)
wq$Date<- as.POSIXct(wq$Date, tz="EST",usetz=TRUE)
wq<-wq %>% 
  filter((Site == 9))

```


```{r winddata, include= FALSE }
wind17<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2017)
wind18<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2018)

winddatatable17<- data.frame(wind17$data)
winddatatable18<- data.frame(wind18$data)

colnames(winddatatable17) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")
colnames(winddatatable18) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")

winddatatable17$Date <- as.POSIXct(as.Date(winddatatable17$Date,origin= "1899-12-30"))
winddatatable18$Date <- as.POSIXct(as.Date(winddatatable18$Date,origin= "1899-12-30"))

windcomb<- rbind(winddatatable17,winddatatable18) 
```


```{r dis, warning= FALSE,  message=FALSE, results="hide" , include=FALSE}

#Station to analyze, can be changed to another station
station = '02323500'   

#Get site name to use in plot titles and such
stinfo  = siteInfo(station)

#Read entire time series, might take several minutes
dis   = importDVs(staid=station,code='00060',stat='00003', sdate= "1950-01-01") 

#Getting some date components
dis$year    = as.numeric(strftime(dis$dates,format="%Y"))
dis$month   = as.numeric(strftime(dis$dates,format="%m")) 

```


```{r discol, warning= FALSE,  message=FALSE, results="hide", include=FALSE}

#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(dis) <- c("StaID", "Discharge", "oldDate", "QualCode", "Year", "Month")
head(dis)

#Changing the format of the dates to be able to plot against time
dis$Date <- as.POSIXct(as.Date(dis$oldDate,origin= "1899-12-30"))

```

```{r r_plots, include= FALSE}
var <-
  ggplot(data= windcomb, aes(x=Date)) +
  labs(x= "Date", y= "") +
  ggtitle("Temp(C),Salinity(ppt),Discharge(1,000 cfs),Mean Wind Speed (ms/c)") +
  stat_summary(mapping= aes(y=Wind_Speed), fun.y="mean", geom="line", color= "gray34", size=2) +
  geom_line(data= dis, aes(y=Discharge/1000), color= "cornflowerblue", size=2) +
  geom_point(data= wq, aes(y= Temperature), color= "red", size=.5) +
  geom_point(data= wq,aes(y= Salinity), color= "black", size=.5) +
  guides(fill= guide_legend(show= TRUE, title="Measurement", override.aes= list(colour= c("cornflowerblue", "black", "red"), size=5))) +
  scale_y_continuous(limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-07-30"))) +
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=12,face="bold"),
        axis.text.x = element_text(size=8))



var<- ggplotly(var)
```

```{r plotly_plot, echo=FALSE, fig.width=8,fig.height=6, warning= FALSE,  message=FALSE}
var
```
