---
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library("cowplot")
library("dplyr")
library("ggplot2")
library("grid")
library("ggthemes")
library("lattice")
library("lubridate")
library("marelac")
library("ncdf4")
library("rnoaa")
library("plotly")
library("scales")
library("tidyverse")
library("waterData")
```

#Site 4
####Longitude:  -83.09211
####Latitude:    29.23017

The main plot consists of continuous data gathered from a Star-Oddi sensor, which measures salinity, temperature, and conductivity hourly, as of August 2017.       
Water discharge data are provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).             
Wind speed data are provided by package `rnoaa`.                
There are discrete measurements for this site.  All discrete measurements were processed by Lakewatch UF.                
This figure is available for zoomability.          


```{r r_site, include= FALSE}
##### Site 1 Analysis with Diver sensor

wq <- read.csv("data/wq.csv", header= T)
wq$Date<- as.POSIXct(wq$Date, tz="EST",usetz=TRUE)
wq<-wq %>% 
  filter((Site == 4))

```


```{r winddata, include= FALSE }
wind17<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2017)
wind18<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2018)

winddatatable17<- data.frame(wind17$data)
winddatatable18<- data.frame(wind18$data)

colnames(winddatatable17) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")
colnames(winddatatable18) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")

winddatatable17$Date <- as.POSIXct(as.Date(winddatatable17$Date,origin= "1899-12-30"))
winddatatable18$Date <- as.POSIXct(as.Date(winddatatable18$Date,origin= "1899-12-30"))

windcomb<- rbind(winddatatable17,winddatatable18) 
```


```{r labresults, include=FALSE, eval=TRUE}
lab <- read.csv("data/discrete_measurement.csv", header= T)

colnames(lab) <- c("Site", "Date", "Time_org", "Time_UTC", "Sun_code", "Phosphorus", "Nitrogen", "Chlorophyll", "Secchi", "Color", "DO", "Temperature","Conductivity", "Salinity", "Depth", "Sensor_Type")

lab$Secchi<- (lab$Secchi/ 3.28)

lab<- lab %>%
  filter(Sensor_Type == "lakewatch")

lab$Date <- as.POSIXct(as.Date(lab$Date,origin= "1899-12-30"))

lab<-lab %>% 
  filter((Site == 4))%>%
  select(Site, Date, Phosphorus, Nitrogen, Chlorophyll, Secchi, Color, Conductivity)

keycol <- "Variable"
valuecol <- "Measurement"
gathercols <- c("Phosphorus", "Nitrogen", "Chlorophyll", "Secchi", "Color", "Conductivity")

lab2<-gather_(lab, keycol, valuecol, gathercols)

```

```{r dis, warning= FALSE,  message=FALSE, results="hide" , include=FALSE}

#Station to analyze, can be changed to another station
station = '02323500'   

#Get site name to use in plot titles and such
stinfo  = siteInfo(station)

#Read entire time series, might take several minutes
dis   = importDVs(staid=station,code='00060',stat='00003', sdate= "1950-01-01") 

#Getting some date components
dis$year    = as.numeric(strftime(dis$dates,format="%Y"))
dis$month   = as.numeric(strftime(dis$dates,format="%m")) 

```


```{r discol, warning= FALSE,  message=FALSE, results="hide", include=FALSE}

#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(dis) <- c("StaID", "Discharge", "oldDate", "QualCode", "Year", "Month")
head(dis)

#Changing the format of the dates to be able to plot against time
dis$Date <- as.POSIXct(as.Date(dis$oldDate,origin= "1899-12-30"))

```

```{r r_plots, include= FALSE}

phos <-
  ggplot(data= lab, aes(x= Date)) +
  ggtitle("Phosphorus") +
  labs(x= "Date", y= "Phosphorus (µg/L)") +
  geom_line(data= dis, aes(y=Discharge/160), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Phosphorus),color= "black", size=3) +
  scale_y_continuous(sec.axis = sec_axis(~.*160,name = "River Discharge (cfs)"),limits=c(0,125)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2018-04-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

nitro <-
  ggplot(data= lab, aes(x= Date)) +
  ggtitle("Nitrogen") +
  labs(x= "Date", y= "Nitrogen (µg/L)") +
  geom_line(data= dis, aes(y=Discharge/13), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Nitrogen),color= "black", size=3) +
   scale_y_continuous(sec.axis = sec_axis(~.*13,name = "River Discharge (cfs)"),limits=c(0,1500)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2018-04-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

chloro <-
ggplot(data= lab, aes(x= Date)) +
  ggtitle("Chlorophyll") +
  labs(x= "Date", y= "Chlorophyll (µg/L)") +
  geom_line(data= dis, aes(y=Discharge/250), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Chlorophyll),color= "black", size=3) +
  scale_y_continuous(sec.axis = sec_axis(~.*250,name = "River Discharge (cfs)"),limits=c(0,80)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2018-04-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))


secchi <-
  ggplot(data= lab, aes(x= Date)) +
  ggtitle("Secchi") +
  labs(x= "Date", y= "Secchi (ft)") +
  geom_line(data= dis, aes(y=Discharge/10000), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Secchi),color= "black", size=3) +
   scale_y_continuous(sec.axis = sec_axis(~.*10000,name = "River Discharge (cfs)"),limits=c(0,2)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2018-04-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

color <-
  ggplot(data= lab, aes(x= Date)) +
  ggtitle("Color") +
  labs(x= "Date", y= "Color(Pt-Co Units)") +
  geom_line(data= dis, aes(y=Discharge/160), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Color),color= "black", size=3) +
  scale_y_continuous(sec.axis = sec_axis(~.*160,name = "River Discharge (cfs)"),limits=c(0,125)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2018-04-30")))+
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

cond <-
  ggplot(data= lab, aes(x= Date)) +
  ggtitle("Conductivity") +
  labs(x= "Date", y= "Conductivity (mS/cm)") +
  geom_line(data= dis, aes(y=Discharge/500), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Conductivity),color= "black", size=3) +
   scale_y_continuous(sec.axis = sec_axis(~.*500,name = "River Discharge (cfs)"),limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2018-04-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))
  

var <-
  ggplot(data= windcomb, aes(x=Date)) +
  labs(x= "Date", y= "") +
  ggtitle("Temp(C),Salinity(ppt),Discharge(1,000 cfs),Mean Wind Speed (ms/c)") +
  stat_summary(mapping= aes(y=Wind_Speed), fun.y="mean", geom="line", color= "gray34", size=2) +
  geom_line(data= dis, aes(y=Discharge/1000), color= "cornflowerblue", size=2) +
  geom_point(data= wq, aes(y= Temperature), color= "red", size=.5) +
  geom_point(data= wq,aes(y= Salinity), color= "black", size=.5) +
  guides(fill= guide_legend(show= TRUE, title="Measurement", override.aes= list(colour= c("cornflowerblue", "black", "red"), size=5))) +
  scale_y_continuous(limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("8 weeks") ,
    labels = date_format("%y/%m"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-07-30"))) +
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=12,face="bold"),
        axis.text.x = element_text(size=8))



var<- ggplotly(var)
```

```{r plotly_plot, echo=FALSE, fig.width=8,fig.height=6, warning= FALSE,  message=FALSE}
var
```

```{r lab _results, echo=FALSE, fig.width=8,fig.height=6, warning= FALSE,  message=FALSE}
plot_grid(phos, nitro,color,cond,secchi, chloro, ncol=2)
```
