---
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(cowplot)
library(ggplot2)
library(ggpubr)
library(grid)
library(gridExtra)
library(lattice)
library(marelac)
library(plotly)
library(scales)
library(rnoaa)
library(plyr)
library(ncdf4)
library(lubridate)
library(dplyr)
library(data.table)
library(colorspace)
library(waterData)
library(hydroTSM)
```

#Site 2
####Longitude:  -83.09591
####Latitude:    29.24560 

The main plot consists of continuous data gathered from a Star-Oddi sensor, which measures salinity, temperature, and conductivity hourly, since August 2017.        
Water discharge data are provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).         
Wind speed data are provided by package `rnoaa`.            
There are discrete measurements for this site.  All discrete measurements were processed by Lakewatch UF.            
This figure is available for zoomability.      

```{r r_site2, include= FALSE}
#####Site 2 Analysis with Star Oddi sensor
LC_WQ2 <- read.csv("data/LC_WQ2_All_Days_R.csv", header= T)

#Naming columns, using the Star Oddi software, records different measurements than the Star Oddi, date, temperature, salinity, conducitivity, sound/velocity
colnames(LC_WQ2) <- c("DateTime_Serial", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
head(LC_WQ2)

#Changing the format of the dates to plot
LC_WQ2$Date <- as.POSIXct(as.Date(LC_WQ2$DateTime_Serial,origin= "1899-12-30"))

#Star-Oddi time is off by 8 hours 
LC_WQ2$Date<- LC_WQ2$Date - 8*60*60

#Calculating salinity, using package `marelac` for this conversion, even though the Diver sensor salinity, we want to standardize the salinity by calculating it with the temperature and conductivity
standard= 42.914
LC_WQ2$Salinity <- convert_RtoS(LC_WQ2$Conductivity/standard, 
                                t= LC_WQ2$Temperature, p=0)

```


```{r winddata, include= FALSE }
wind17<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2017)
wind18<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2018)

winddatatable17<- data.frame(wind17$data)
winddatatable18<- data.frame(wind18$data)

colnames(winddatatable17) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")
colnames(winddatatable18) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")

winddatatable17$Date <- as.POSIXct(as.Date(winddatatable17$Date,origin= "1899-12-30"))
winddatatable18$Date <- as.POSIXct(as.Date(winddatatable18$Date,origin= "1899-12-30"))

windcomb<- rbind(winddatatable17,winddatatable18) 
```


```{r labresults, include=FALSE, eval=TRUE}
labresults <- read.csv("data/2017_lakewatch_labresults.csv", header= T)

#Creating new column names
colnames(labresults) <- c("County", "Name", "oldDate", "Month", "Day","Year","Station", "Phosphorus", "Nitrogen", "Chlorophyll", "Secchi", "Secchi 2", "Color", "SpecificConductancemicro", "SpecificConductancemilli")

labresults$Date <- as.POSIXct(as.Date(labresults$oldDate, origin= "1899-12-30"))

labresults$Date <- as.POSIXct(as.Date(labresults$oldDate, "%m/%d/%Y"))

#create new column for the micro and milli siemens in Specific Conductance
#1 millisiemens [mS] = 1000 microsiemens [??S, uS]

labresults$SpecificConductancemilli<- (labresults$SpecificConductancemilli / 100)

labresults$Conductivity<-NA

labresults$Conductivity<-paste(labresults$SpecificConductancemilli,labresults$SpecificConductancemicro)

labresults$Conductivity<-as.numeric(gsub('NA','',labresults$Conductivity))

labresults$Secchi<- (labresults$Secchi/ 3.28)


#Subsetting the data into 
site1<-subset(labresults,Station=="1")
site2<-subset(labresults,Station=="2")
site3<-subset(labresults,Station=="3")
site4<-subset(labresults,Station=="4")
site5<-subset(labresults,Station=="5")
site6<-subset(labresults,Station=="6")

```

```{r r_RD, include=FALSE}
#This is the river discharge data from the package `waterData`

#station to analyze
station = '02323500'   

#get site name to use in plot titles and such
stinfo  = siteInfo(station)

#read entire time series
dis   = importDVs(staid=station,code='00060',stat='00003', sdate= "1950-01-01") 
#ok looks like temp code is wrong for this station, maybe rainfall is available?

#get some date components
dis$year    = as.numeric(strftime(dis$dates,format="%Y"))
dis$month   = as.numeric(strftime(dis$dates,format="%m")) 

```

```{r RD_Date, include= FALSE}
#### River Discharge, this data was gathered from the River Discharge R file, and retrieved that way, the information is in the Rhistory for this analysis
head(dis)

#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(dis) <- c("StaID", "Discharge", "oldDate", "QualCode", "Year", "Month")
head(dis)

#Changing the format of the dates to be able to plot against time
dis$Date <- as.POSIXct(as.Date(dis$oldDate,origin= "1899-12-30"))

```


```{r r_var2, include= FALSE}

phos2 <-
  ggplot(data= site2, aes(x= Date)) +
  ggtitle("Phosphorus") +
  labs(x= "Date", y= "Phosphorus (µg/L)& Discharge/160") +
  geom_line(data= dis, aes(y=Discharge/160), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Phosphorus),color= "black", size=3) +
  scale_y_continuous(limits=c(0,125)) +
  scale_x_datetime(
    breaks = date_breaks("month") ,
    labels = date_format("%m/%y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2017-12-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

nitro2 <-
  ggplot(data= site2, aes(x= Date)) +
  ggtitle("Nitrogen") +
  labs(x= "Date", y= "Nitrogen (µg/L)& Discharge/13") +
  geom_line(data= dis, aes(y=Discharge/13), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Nitrogen), color= "black", size=3) +
  scale_y_continuous(limits=c(0,1500)) +
  scale_x_datetime(
    breaks = date_breaks("month") ,
    labels = date_format("%m/%y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2017-12-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

chloro2 <-
ggplot(data= site2, aes(x= Date)) +
  ggtitle("Chlorophyll") +
  labs(x= "Date", y= "Chlorophyll (µg/L)& Discharge/250") +
  geom_line(data= dis, aes(y=Discharge/250), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Chlorophyll),color= "black", size=3) +
  scale_y_continuous(limits=c(0,80)) +
  scale_x_datetime(
    breaks = date_breaks("month") ,
    labels = date_format("%m/%y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2017-12-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))


secchi2 <-
  ggplot(data= site2, aes(x= Date)) +
  ggtitle("Secchi") +
  labs(x= "Date", y= "Secchi (ft)& Discharge/4000") +
  geom_line(data= dis, aes(y=Discharge/4000), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Secchi),color= "black", size=3) +
  scale_y_continuous(limits=c(0,5)) +
  scale_x_datetime(
    breaks = date_breaks("month") ,
    labels = date_format("%m/%y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2017-12-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

color2 <-
  ggplot(data= site2, aes(x= Date)) +
  ggtitle("Color") +
  labs(x= "Date", y= "Color(Pt-Co Units)& Discharge/160") +
  geom_line(data= dis, aes(y=Discharge/160), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Color),color= "black", size=3) +
  scale_y_continuous(limits=c(0,125)) +
  scale_x_datetime(
    breaks = date_breaks("month") ,
    labels = date_format("%m/%y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2017-12-30")))+
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))

cond2 <-
  ggplot(data= site2, aes(x= Date)) +
  ggtitle("Specific Conductance") +
  labs(x= "Date", y= "Conductivity (mS/cm)& Discharge/40") +
  geom_line(data= dis, aes(y=Discharge/500), color= "cornflowerblue", size=1) +
  geom_point(aes(y=Conductivity),color= "black", size=3) +
  scale_y_continuous(limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("month") ,
    labels = date_format("%m/%y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2016-12-25"),
      as.POSIXct("2017-12-30")))+ 
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=8,face="bold"),
        axis.text.x = element_text(size=6))
  

var2 <-
  ggplot(data= windcomb, aes(x=Date)) +
  labs(x= "Date", y= "Temp(C),Salinity(ppt),Discharge (1,000 cfs),Wind Speed (ms/c)") +
  stat_summary(mapping= aes(y=Wind_Speed), fun.y="mean", geom="line", color= "gray34", size=2) +
  geom_line(data= dis, aes(y=Discharge/1000), color= "cornflowerblue", size=2) +
  geom_point(data= LC_WQ2, aes(y= Temperature), color= "red", size=.5) +
  geom_point(data= LC_WQ2,aes(y= Salinity), color= "black", size=.5) +
  guides(fill= guide_legend(show= TRUE, title="Measurement", override.aes= list(colour= c("cornflowerblue", "black", "red"), size=5))) +
  scale_y_continuous(limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("4 weeks") ,
    labels = date_format("%m/%Y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-05-05"))) +
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=12,face="bold"),
        axis.text.x = element_text(size=8))
#test


var2<- ggplotly(var2)
#cond2<- ggplotly(cond2)
#color2<- ggplotly(color2)
#secchi2<- ggplotly(secchi2)
#chloro2<- ggplotly(chloro2)
#nitro2<- ggplotly(nitro2)
#phos2<- ggplotly(phos2)
```

```{r finalplot, echo=FALSE, fig.width=8,fig.height=6, warning= FALSE,  message=FALSE}

var2
```


```{r condplot, echo=FALSE, warning= FALSE,  message=FALSE, fig.width=12,fig.height=10,}

par(mfrow=c(3,2)) 

plot(x=dis$Date, y=dis$Discharge, ylab="", lwd= 4, xlab= "Date", main= "",ylim=c(0,40000), axes=FALSE,xlim = c(as.POSIXct("2017-01-01"),as.POSIXct("2017-12-31")), type="l",col="cornflowerblue")
axis(4, at=pretty(c(0,40000)), col='black')
par(new=TRUE)
plot(site2$Date, site2$Phosphorus, pch=19, ylab="Phosphorus (µg/L)", xlab="Date", main="Phosphorus", ylim=c(0,125),format="%m-%Y",las=1, cex=2)
#polygon(xx,yy,col="cornflowerblue", border=NA)
mtext("River Discharge ( cfs)", side = 4,cex=0.6)

plot(x=dis$Date, y=dis$Discharge, ylab="", lwd= 4, xlab= "Date", main= "",ylim=c(0,40000), axes=FALSE,xlim = c(as.POSIXct("2017-01-01"),as.POSIXct("2017-12-31")), type="l",col="cornflowerblue")
axis(4, at=pretty(c(0,40000)), col='black')
par(new=TRUE)
plot(site2$Date, site2$Nitrogen, pch=19, ylab="Nitrogen (µg/L)", xlab="Date", main="Nitrogen", ylim=c(0,1300),format="%m-%Y",las=1, cex=2)
#polygon(xx,yy,col="cornflowerblue", border=NA)
mtext("River Discharge ( cfs)", side = 4,cex=0.6)

plot(x=dis$Date, y=dis$Discharge, ylab="", lwd= 4, xlab= "Date", main= "",ylim=c(0,40000), axes=FALSE,xlim = c(as.POSIXct("2017-01-01"),as.POSIXct("2017-12-31")), type="l",col="cornflowerblue")
#polygon(xx,yy,col="cornflowerblue", border=NA)
axis(4, at=pretty(c(0,40000)), col='black')
par(new=TRUE)
plot(site2$Date, site2$Chlorophyll, pch=19, ylab="Chlorophyll (µg/L)", xlab="Date", main="Chlorophyll ", ylim=c(0,65),format="%m-%Y",las=1, cex=2)
mtext("River Discharge ( cfs)", side = 4,cex=0.6)

plot(x=dis$Date, y=dis$Discharge, ylab="", lwd= 4, xlab= "Date", main= "",ylim=c(0,40000), axes=FALSE,xlim = c(as.POSIXct("2017-01-01"),as.POSIXct("2017-12-31")), type="l",col="cornflowerblue")
#polygon(xx,yy,col="cornflowerblue", border=NA)
axis(4, at=pretty(c(0,40000)), col='black')
par(new=TRUE)
plot(site2$Date, site2$Secchi, pch=19, ylab="Secchi (m)", xlab="Date", main="Secchi", ylim=c(0,2),format="%m-%Y",las=1, cex=2)
mtext("River Discharge ( cfs)", side = 4,cex=0.6)

plot(x=dis$Date, y=dis$Discharge, ylab="", lwd= 4, xlab= "Date", main= "",ylim=c(0,40000), axes=FALSE,xlim = c(as.POSIXct("2017-01-01"),as.POSIXct("2017-12-31")), type="l",col="cornflowerblue")
#polygon(xx,yy,col="cornflowerblue", border=NA)
axis(4, at=pretty(c(0,40000)), col='black')
par(new=TRUE)
plot(site2$Date, site2$Color, pch=19, ylab="Color (Pt-Co Units)", xlab="Date", main="Color", ylim=c(0,110),format="%m-%Y",las=1, cex=2)
mtext("River Discharge ( cfs)", side = 4,cex=0.6)

plot(x=dis$Date, y=dis$Discharge, ylab="", lwd= 4, xlab= "Date", main= "",ylim=c(0,40000), axes=FALSE,xlim = c(as.POSIXct("2017-01-01"),as.POSIXct("2017-12-31")), type="l",col="cornflowerblue")
#polygon(xx,yy,col="cornflowerblue", border=NA)
axis(4, at=pretty(c(0,40000)), col='black')
par(new=TRUE)
plot(site2$Date, site2$Conductivity, pch=19, ylab="Conductivity (mS/cm))", xlab="Date", main="Conductivity", ylim=c(0,40),format="%m-%Y",las=1, cex=2)
mtext("River Discharge ( cfs)", side = 4,cex=0.6)


```
