---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(cowplot)
library(devtools)
library(ggplot2)
library(ggpubr)
library(grid)
library(gridExtra)
library(lattice)
library(marelac)
library(plotly)
library(scales)
library(rnoaa)
library(plyr)
library(ncdf4)
library(lubridate)
library(dplyr)
library(scales)
library(data.table)
library(colorspace)
library(waterData)
library(hydroTSM)
```

#Site 9
####Longitude:  -83.08271
####Latitude:    29.23215


The main plot consists of continuous data gathered from a Star-Oddi sensor, which measures salinity, temperature, and conductivity hourly, since November 2017.           
Water discharge data are provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).                    
Wind speed data are provided by package `rnoaa`.                       
There no are discrete measurements for this site.         
This figure is available for zoomability.     

```{r r_site9, include= FALSE}
#####Site 9 Analysis with Star Oddi
LC_WQ9 <- read.csv("data/LC_WQ9_All_Days_R.csv", header= T)

#Naming columns, using the Star Oddi software, records different measurements than the Star Oddi, date, temperature, salinity, conducitivity, sound/velocity
colnames(LC_WQ9) <- c("newDate", "Temperature", "Salinity", "Conductivity", "Sound/Velocity")
head(LC_WQ9)

#Changing the format of the dates to plot
LC_WQ9$Date <- as.POSIXct(as.Date(LC_WQ9$newDate,origin= "1899-12-30"))

LC_WQ9$Date<- LC_WQ9$Date - 8*60*60


#Calculating salinity, using package `marelac` for this conversion, even though the Diver sensor salinity, we want to standardize the salinity by calculating it with the temperature and conductivity
standard= 42.914
LC_WQ9$Salinity <- convert_RtoS(LC_WQ9$Conductivity/standard, 
                                t= LC_WQ9$Temperature, p=0)

```

```{r winddata, include= FALSE }
wind17<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2017)
wind18<-buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2018)

winddatatable17<- data.frame(wind17$data)
winddatatable18<- data.frame(wind18$data)

colnames(winddatatable17) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")
colnames(winddatatable18) <- c("Date", "Lat", "Lon", "Direction", "Wind_Speed")

winddatatable17$Date <- as.POSIXct(as.Date(winddatatable17$Date,origin= "1899-12-30"))
winddatatable18$Date <- as.POSIXct(as.Date(winddatatable18$Date,origin= "1899-12-30"))

windcomb<- rbind(winddatatable17,winddatatable18) 
```

```{r r_RD, include=FALSE}
#This is the river discharge data from the package `waterData`

#station to analyze
station = '02323500'   

#get site name to use in plot titles and such
stinfo  = siteInfo(station)

#read entire time series
dis   = importDVs(staid=station,code='00060',stat='00003', sdate= "1950-01-01") 
#ok looks like temp code is wrong for this station, maybe rainfall is available?

#get some date components
dis$year    = as.numeric(strftime(dis$dates,format="%Y"))
dis$month   = as.numeric(strftime(dis$dates,format="%m")) 

#make dataset from epochs, 
disE  = dis[dis$dates>='1950-01-01' & dis$dates<='2017-10-01',]  

#get monthly sum, mean, sd, and var
#discharge
disE.mo  = aggregate(val~month+year,data=disE,FUN = function(x) c(mean(x,na.rm=T),sd(x,na.rm=T),var(x,na.rm=T),sum(x)))
disE.mo  = do.call('data.frame',disE.mo)
names(disE.mo)[3:6] = c('avg','sd','var','sumflow') 
disE.mo$yrmo = disE.mo$year+(disE.mo$month-0.5)/12       


#get yearly mean, sd, and var
#discharge
disE.yr  = aggregate(val~year,data=disE,FUN = function(x) c(mean(x,na.rm=T),sd(x,na.rm=T),var(x,na.rm=T)))
disE.yr  = do.call('data.frame',disE.yr)
names(disE.yr)[2:4] = c('avg','sd','var')                      

disE.mo.ts  = ts(disE.mo$avg,start=c(1950,1),end=c(2017,10),frequency=12)
disE.mo.sum.ts  = ts(disE.mo$sumflow,start=c(1950,1),end=c(2017,10),frequency=12)
disE.yr.ts  = ts(disE.yr$avg,start=1950,end=2017,frequency=1)

```

```{r RD_newdate, include= FALSE}
#### River Discharge, this data was gathered from the River Discharge R file, and retrieved that way, the information is in the Rhistory for this analysis
head(dis)

#Naming columns, using the Diver sensors, collects date, pressure, temp, conductivity
colnames(dis) <- c("StaID", "Discharge", "newDate", "QualCode", "Year", "Month")
head(dis)

#Changing the format of the dates to be able to plot against time
dis$Date <- as.POSIXct(as.Date(dis$newDate,origin= "1899-12-30"))

```

```{r r_var9, include= FALSE}
var9 <-
  ggplot(data= windcomb, aes(x=Date)) +
  labs(x= "Date", y= "Temp(C),Salinity(ppt),Discharge (1,000 cfs),Wind Speed (ms/c)") +
  stat_summary(mapping= aes(y=Wind_Speed), fun.y="mean", geom="line", color= "gray34", size=2) +
  geom_line(data= dis, aes(y=Discharge/1000), color= "cornflowerblue", size=2) +
  geom_point(data= LC_WQ9, aes(y= Temperature), color= "red", size=.5) +
  geom_point(data= LC_WQ9,aes(y= Salinity), color= "black", size=.5) +
  guides(fill= guide_legend(show= TRUE, title="Measurement", override.aes= list(colour= c("cornflowerblue", "black", "red"), size=5))) +
  scale_y_continuous(limits=c(0,40)) +
  scale_x_datetime(
    breaks = date_breaks("4 weeks") ,
    labels = date_format("%m/%Y"),
    expand = c(0, 0),
    limits = c(
      as.POSIXct("2017-08-10"),
      as.POSIXct("2018-05-05"))) +
  theme(panel.border = element_rect(color = "black", size = 0.5, fill = NA, linetype="solid"),
        axis.title=element_text(size=12,face="bold"),
        axis.text.x = element_text(size=8))



var9<- ggplotly(var9)

```
```{r finalplot, echo=FALSE, fig.width=8,fig.height=6, warning= FALSE,  message=FALSE}

var9
```
